ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
filled the table

    \begin{table}[!t]
        \processtable{Centromeres extraction comparison using \odgi\ and VG
        \label{tab:02}} {
            \begin{tabular}{@{}lllll@{}}
                \toprule Operation & Tool & Runtime (mm:ss) & Memory (GB) & Output size (GB) \\
                \midrule
                row1               & row1 & row1            & row1        & row1             \\
                row2               & row2 & row2            & row2        & row2             \\
                row3               & row3 & row3            & row3        & row3             \\
                row4               & row4 & row4            & row4        & row4             \\
                \botrule
            \end{tabular}}

>>>>

    %TODO to repeat on a bigger machine to avoid vg crashing
    \begin{table}[!t]
        \processtable{Centromeres extraction comparison using \odgi\ and VG
        \label{tab:02}} {
            \begin{tabular}{@{}lllll@{}}
                \toprule Operation & Tool & Runtime (mm:ss) & Memory (GB) & Output size (GB)    \\
                \midrule
                Format conversion                           &       &       &                   \\
                                    & \cmd{odgi build}      & 1:35  & 10.39 & 5.4               \\
                                    & \cmd{vg convert}      & 8:14  & 28.43 & 6.1               \\
                Subgraph extraction                         &       &       &                   \\
                                    & \cmd{odgi extract}    & 1:15  & 9.43  & 2.7               \\
                                    & \cmd{vg chunk}        & 21:09 & 59.33 & 1.7               \\
                \botrule
            \end{tabular}}
